Differential expression analysis of reprocessed AMPAD RNASeq data (All 7 brain regions with CQN normlaisation and BIC based model selection)

### 2017-07-07 code/Rmd/ALL_REPROCESSED.Rmd
Minor bug fix

covariates$ROSMAP = covariates$ROSMAP %>%
  dplyr::mutate(SampleID = as.character(SampleID),
                BrainRegion = 'DLPFC',
                BrainRegion.Diagnosis = factor(paste(BrainRegion, Diagnosis, sep = '.')),
                msex = factor(msex, labels = c('1'='MALE','0'='FEMALE')),
                Batch = factor(Batch)) %>%
  dplyr::rename(Gender = msex, RIN = RINcontinuous, AOD = age_death, PMI = pmi) %>%
  dplyr::select(SampleID, BrainRegion.Diagnosis, Batch, Gender, AOD, PMI, RIN, PCT_PF_READS_ALIGNED, 
                PCT_CODING_BASES, PCT_INTERGENIC_BASES, PCT_INTRONIC_BASES, PCT_RIBOSOMAL_BASES)
covariates$ROSMAP$individualIdentifier = factor(paste0('ROSMAPpseudoid',1:dim(covariates$ROSMAP)[1]))

covariates$MSBB = covariates$MSBB %>%
  dplyr::mutate(SampleID = as.character(SampleID),
                individualIdentifier = factor(paste0('BB',individualIdentifier)),
                SEX = factor(SEX, labels = c('M'='MALE','F'='FEMALE')),
                batch = factor(batch),
                PMI = PMI/60) %>%
  dplyr::rename(Batch = batch, Gender = SEX) %>%
  dplyr::select(SampleID, BrainRegion.Diagnosis, individualIdentifier, Batch, Gender, AOD, PMI, RIN, 
                PCT_PF_READS_ALIGNED, PCT_CODING_BASES, PCT_INTERGENIC_BASES, PCT_INTRONIC_BASES, PCT_RIBOSOMAL_BASES)

covariates$MAYO = covariates$MAYO %>%
  dplyr::mutate(SampleID = as.character(SampleID),
                Donor_ID = factor(paste0('MAYO', Donor_ID)),
                Gender = factor(Gender, labels = c('M'='MALE','F'='FEMALE')),
                Batch = factor(Source)) %>%
  dplyr::rename(individualIdentifier = Donor_ID, AOD = AgeAtDeath) %>%
  dplyr::select(SampleID, BrainRegion.Diagnosis, individualIdentifier, Batch, Gender, AOD, PMI, RIN, 
                PCT_PF_READS_ALIGNED, PCT_CODING_BASES, PCT_INTERGENIC_BASES, PCT_INTRONIC_BASES, PCT_RIBOSOMAL_BASES)

@@

# Intronic Rate
p[[4]] = ggplot(COVARIATES, aes(x = BrainRegion, y = PCT_INTRONIC_BASES, color = Study, fill = Diagnosis)) + geom_boxplot()
p[[4]] = p[[4]] + ggtitle('Intronic Factions') + my.theme

@@

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=BrainRegion, shape=Study, size=RIN))
p <- p + theme_bw() + theme(legend.position="top")
p <- p + geom_text(aes(label= label), size=4, hjust=0)
p

>>>>

covariates$ROSMAP = covariates$ROSMAP %>%
  dplyr::mutate(SampleID = as.character(SampleID),
                BrainRegion = 'DLPFC',
                BrainRegion.Diagnosis = factor(paste(BrainRegion, Diagnosis, sep = '.')),
                msex = factor(msex, levels = c('1', '0'), labels = c('1'='MALE','0'='FEMALE')),
                Batch = factor(Batch)) %>%
  dplyr::rename(Gender = msex, RIN = RINcontinuous, AOD = age_death, PMI = pmi) %>%
  dplyr::select(SampleID, BrainRegion.Diagnosis, Batch, Gender, AOD, PMI, RIN, PCT_PF_READS_ALIGNED, 
                PCT_CODING_BASES, PCT_INTERGENIC_BASES, PCT_INTRONIC_BASES, PCT_RIBOSOMAL_BASES)
covariates$ROSMAP$individualIdentifier = factor(paste0('ROSMAPpseudoid',1:dim(covariates$ROSMAP)[1]))

covariates$MSBB = covariates$MSBB %>%
  dplyr::mutate(SampleID = as.character(SampleID),
                individualIdentifier = factor(paste0('BB',individualIdentifier)),
                SEX = factor(SEX, levels = c('M', 'F'), labels = c('M'='MALE','F'='FEMALE')),
                batch = factor(batch),
                PMI = PMI/60) %>%
  dplyr::rename(Batch = batch, Gender = SEX) %>%
  dplyr::select(SampleID, BrainRegion.Diagnosis, individualIdentifier, Batch, Gender, AOD, PMI, RIN, 
                PCT_PF_READS_ALIGNED, PCT_CODING_BASES, PCT_INTERGENIC_BASES, PCT_INTRONIC_BASES, PCT_RIBOSOMAL_BASES)

covariates$MAYO = covariates$MAYO %>%
  dplyr::mutate(SampleID = as.character(SampleID),
                Donor_ID = factor(paste0('MAYO', Donor_ID)),
                Gender = factor(Gender, levels = c('M', 'F'), labels = c('M'='MALE','F'='FEMALE')),
                Batch = factor(Source)) %>%
  dplyr::rename(individualIdentifier = Donor_ID, AOD = AgeAtDeath) %>%
  dplyr::select(SampleID, BrainRegion.Diagnosis, individualIdentifier, Batch, Gender, AOD, PMI, RIN, 
                PCT_PF_READS_ALIGNED, PCT_CODING_BASES, PCT_INTERGENIC_BASES, PCT_INTRONIC_BASES, PCT_RIBOSOMAL_BASES)

@@

# Intronic Rate
p[[4]] = ggplot(COVARIATES, aes(x = BrainRegion, y = PCT_INTRONIC_BASES, color = Study, fill = Diagnosis)) + geom_boxplot()
p[[4]] = p[[4]] + ggtitle('Intronic Fractions') + my.theme

@@

sdev = round((PC$sdev^2/sum(PC$sdev^2)) * 100, 0)

p <- ggplot(plotdata, aes(x=PC1, y=PC2))
p <- p + geom_point(aes(color=BrainRegion, shape=Study, size=RIN))
p <- p + theme_bw() + theme(legend.position="top") + ylab(paste0('PC1(',sdev[2],'%)')) + xlab(paste0('PC1(',sdev[1],'%)'))
p <- p + geom_text(aes(label= label), size=4, hjust=0)
p
